R Notebook

### 2019-08-26 Cytokine_Analysis.Rmd
proportions of tf cells making cytokine

CD4<-plot_filter(read.csv("ICS_CD4_Cytokine_clean.csv"))

CD8<-plot_filter(read.csv("ICS_CD8_Cytokine_clean.csv"))

MFI<-plot_filter(read.csv("ICS_CD4_MFI_clean.csv"))

Compass<-plot_filter(read.csv("ICS_Compass_scores_complete_clean.csv"))

GD<-plot_filter(read.csv("ICS_GD_Cytokine_clean.csv"))

@@

##PMA & Ionomycin
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PMA") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

##Whole Cell Lysate
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="WCL") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

##CFP-10 & ESAT-6
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_4(a, col)
    if(dim(b)[1]!=0)
    print(kable(b, caption=col)) #will return the output for each character string in the loop
}
```

>>>>

CD4<-read.csv("ICS_CD4_Cytokine_clean.csv")

CD8<-read.csv("ICS_CD8_Cytokine_clean.csv")

MFI<-read.csv("ICS_CD4_MFI_clean.csv")

Compass<-read.csv("ICS_Compass_scores_complete_clean.csv")

GD<-read.csv("ICS_GD_Cytokine_clean.csv")

@@

##PMA & Ionomycin
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PMA") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0){
    print(kable(b, caption=col))#will return the output for each character string in the loop
    y<-plot_with_all_stats(a, col)+labs(title=col)
    print(y)}
    }
```

##Whole Cell Lysate
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="WCL") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0){
    print(kable(b, caption=col))#will return the output for each character string in the loop
    y<-plot_with_all_stats(a, col)+labs(title=col)
    print(y)}
    }
```

##CFP-10 & ESAT-6
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col)
    if(dim(b)[1]!=0){
    print(kable(b, caption=col))#will return the output for each character string in the loop
    y<-plot_with_all_stats(a, col)+labs(title=col)
    print(y)}
    }
```

### 2019-08-26 ICS_Cleaning.Rmd
proportions of tf cells making cytokine

l<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_new.csv,
        CD4_phenotype_new.csv, CD4_phenotype.csv, CD4.csv, 
        CD8_Counts.csv, CD8_Cytokine.csv, 
        GD_Counts.csv, GD_Cytokine.csv
        )
l<-lapply(l, function(x) clean_flowjo_output(x))
l<-lapply(l, function(x) splitter(x, "Sample", "_", one="Donor", two="TB", three="SM", four="Stim"))
l<-lapply(l, function(x) fix.names(x))
l<-lapply(l, function(x) remove_samples(x))
l<-lapply(l, function(x) remove_donors(x))
l<-lapply(l, function(x) class_change(x))
l<-lapply(l, function(x) changeTB(x))
l<-lapply(l, function(x) changeHD(x))

@@

```{r update and organize cytokine variables}
#If you want to know the double producers without considering the opposite TH cytokines
library(dplyr)
CD4_Cytokine.csv<-dplyr::mutate(CD4_Cytokine.csv, G_T = G_4_x_T + G_x_13_T + G_x_x_T,
                   IL4_IL13 = G_4_13_x + x_4_13_T + x_4_13_x,
                   TH1.Total = TH1.Freq + TH1.2.Freq,
                   TH2.Total = TH2.Freq + TH1.2.Freq
                   )
```

@@

```{r subtract unstimulated from cyt freq tables}
#the documentation for the background.subtract function is in a script in the miscellaneous folder
#just subtracts the value of the unstim from the value of the stim by donor
filenames = c("CD4_Cytokine.csv", "CD8_Cytokine.csv", "GD_Cytokine.csv")
l<-list(CD4_Cytokine.csv, CD8_Cytokine.csv, GD_Cytokine.csv)
l<-lapply(l, function(x) arrange(x, Donor))
l<-lapply(l, function(x) background.subtract(x, "Donor", "Stim", "UN"))
for (i in 1:length(filenames)) {
    assign(filenames[i], 
           data.frame(l[i]))}
#sets all negative values to zero
CD4_Cytokine.csv[CD4_Cytokine.csv<0]<-0
CD8_Cytokine.csv[CD8_Cytokine.csv<0]<-0
GD_Cytokine.csv[GD_Cytokine.csv<0]<-0
```

@@

```{r write files to "clean" directory}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
write.csv(CD4_Counts.csv, file = "ICS_CD4_Counts_clean.csv")
write.csv(CD4_Cytokine.csv, file = "ICS_CD4_Cytokine_clean.csv")
write.csv(CD4_MFI.csv, file = "ICS_CD4_MFI_clean.csv")
write.csv(CD4_phenotype, file = "ICS_CD4_phenotype_clean.csv")
write.csv(CD4, file = "ICS_CD4_clean.csv")
write.csv(CD8_Counts.csv, file = "ICS_CD8_Counts_clean.csv")
write.csv(CD8_Cytokine.csv, file = "ICS_CD8_Cytokine_clean.csv")
write.csv(GD_Counts.csv, file = "ICS_GD_Counts_clean.csv")
write.csv(GD_Cytokine.csv, file = "ICS_GD_Cytokine_clean.csv")
```

>>>>

l<-list(CD4_Counts.csv, CD4_cytokine_new.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_new.csv,
        CD4_phenotype_new.csv, CD4_phenotype.csv, CD4.csv, 
        CD8_Counts.csv, CD8_Cytokine.csv, 
        GD_Counts.csv, GD_Cytokine.csv
        )
l<-lapply(l, function(x) clean_flowjo_output(x))
l<-lapply(l, function(x) splitter(x, "Sample", "_", one="Donor", two="TB", three="SM", four="Stim"))
l<-lapply(l, function(x) fix.names(x))
l<-lapply(l, function(x) remove_samples(x))
l<-lapply(l, function(x) remove_donors(x))
l<-lapply(l, function(x) class_change(x))
l<-lapply(l, function(x) changeTB(x))
l<-lapply(l, function(x) changeHD(x))

@@

```{r update and organize cytokine variables}
library(dplyr)
CD4_Cytokine<-merge(CD4_Cytokine.csv, CD4_cytokine_new.csv, by=c("Sample","Donor","TB","SM","Stim" ), all=TRUE)
#If you want to know the double producers without considering the opposite TH cytokines
CD4_Cytokine<-dplyr::mutate(CD4_Cytokine, 
         G_T = G_4_x_T + G_x_13_T + G_x_x_T,
         IL4_IL13 = G_4_13_x + x_4_13_T + x_4_13_x,
         TH1.Total = TH1.Freq + TH1.2.Freq,
         TH2.Total = TH2.Freq + TH1.2.Freq
                   )
#To collapse boolean gates in transcription factor exported data
CD4_Cytokine<-dplyr::mutate(CD4_Cytokine, 
        tbet_ifng=  rowSums(CD4_Cytokine[,grep("tbet_G", names(CD4_Cytokine))]),
        tbet_tnfa=  rowSums(CD4_Cytokine
                    [intersect(grep("tbet", names(CD4_Cytokine)) , grep("_T", names(CD4_Cytokine)))]),
        tbet_il4=   rowSums(CD4_Cytokine[,grep("tbet_._4_", names(CD4_Cytokine))]),
        tbet_il13=  rowSums(CD4_Cytokine[,grep("tbet_._._13", names(CD4_Cytokine))]),
        gata3_ifng= rowSums(CD4_Cytokine[,grep("gata3_G", names(CD4_Cytokine))]),
        gata3_tnfa= rowSums(CD4_Cytokine
                    [intersect(grep("gata3", names(CD4_Cytokine)) , grep("_T", names(CD4_Cytokine)))]),
        gata3_il4=  rowSums(CD4_Cytokine[,grep("gata3_._4_", names(CD4_Cytokine))]),
        gata3_il13= rowSums(CD4_Cytokine[,grep("gata3_._._13", names(CD4_Cytokine))])
            )

CD4_Cytokine<-dplyr::mutate(CD4_Cytokine, 
        tbet_th1=  tbet_G_x_x_T + tbet_G_x_x_x + tbet_x_x_x_T,
        tbet_th2=  tbet_x_4_13_x + tbet_x_4_x_x + tbet_x_x_13_x,
        tbet_th1.2=tbet_G_4_13_T + tbet_G_4_13_x + tbet_G_4_x_T + tbet_G_4_x_x + 
            tbet_G_x_13_T + tbet_G_x_13_x + tbet_x_4_13_T + tbet_x_4_x_T + tbet_x_x_13_T,
        gata3_th1=  gata3_G_x_x_T + gata3_G_x_x_x + gata3_x_x_x_T,
        gata3_th2=  gata3_x_4_13_x + gata3_x_4_x_x + gata3_x_x_13_x,
        gata3_th1.2=gata3_G_4_13_T + gata3_G_4_13_x + gata3_G_4_x_T + gata3_G_4_x_x + 
            gata3_G_x_13_T + gata3_G_x_13_x + gata3_x_4_13_T + gata3_x_4_x_T + gata3_x_x_13_T 
            )
```

@@

```{r subtract unstimulated from cyt freq tables}
#the documentation for the background.subtract function is in a script in the miscellaneous folder
#just subtracts the value of the unstim from the value of the stim by donor
filenames = c("CD4_Cytokine", "CD8_Cytokine.csv", "GD_Cytokine.csv")
l<-list(CD4_Cytokine, CD8_Cytokine.csv, GD_Cytokine.csv)
l<-lapply(l, function(x) arrange(x, Donor))
l<-lapply(l, function(x) background.subtract(x, "Donor", "Stim", "UN"))
for (i in 1:length(filenames)) {
    assign(filenames[i], 
           data.frame(l[i]))}
#sets all negative values to zero
CD4_Cytokine[CD4_Cytokine<0]<-0
CD8_Cytokine.csv[CD8_Cytokine.csv<0]<-0
GD_Cytokine.csv[GD_Cytokine.csv<0]<-0
```

@@

```{r write files to "clean" directory}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
write.csv(CD4_Counts.csv, file = "ICS_CD4_Counts_clean.csv")
write.csv(CD4_Cytokine, file = "ICS_CD4_Cytokine_clean.csv")
write.csv(CD4_MFI.csv, file = "ICS_CD4_MFI_clean.csv")
write.csv(CD4_phenotype, file = "ICS_CD4_phenotype_clean.csv")
write.csv(CD4, file = "ICS_CD4_clean.csv")
write.csv(CD8_Counts.csv, file = "ICS_CD8_Counts_clean.csv")
write.csv(CD8_Cytokine.csv, file = "ICS_CD8_Cytokine_clean.csv")
write.csv(GD_Counts.csv, file = "ICS_GD_Counts_clean.csv")
write.csv(GD_Cytokine.csv, file = "ICS_GD_Cytokine_clean.csv")
```
